Do Reddit /r/depression Authors who Pen Suicidal Ideation Leave Reddit at Higher Rates?

### 2016-10-24 Paper_Rough_Draft.Rmd
Redo prosterior calculation with control group.

[give methods overview]

@@

```{r, echo=FALSE, warning=FALSE}
### Load Data
      load(file = "Data/SI_Author_Sample/Author_Summary.RData")
      user.summary = 
            filter(user.summary, recent < 150) %>%
            mutate(t = recent)
      n = user.summary$n
      eps = user.summary$eps
      eps[is.na(eps)] = 0 
      t = user.summary$t
      N = nrow(user.summary)
### Simulate Mu given Data
      alpha = 1; beta = 1
      mu = replicate(n = 10000, rgamma(N, shape = alpha + n, rate = beta + n*eps))
### Now get overall credible interval for sum(Q)
      prior.p = 0.000001
      make.p = function(mu,p) p / (exp(-mu*t)*(1-p) + p)
      post.E = colSums(apply(mu, 2, make.p, p=prior.p))/N * 100
      hist(post.E, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
           xlab="", ylab="")
      ci = quantile(post.E, probs = c(0.025, 0.975))
```

@@

```{r, echo=FALSE, warning=FALSE}
### Calculate P(Q) from Mu and data
      prior.p = c(0.5, 10^-(1:4))
      post_p = sapply(prior.p, FUN = function(x) apply(mu, 2, make.p, p=x) %>% rowMeans)
      colnames(post_p) = c("p.5", paste0("p10.", 1:4))
      user.summary2 = 
            cbind(user.summary, post_p) %>%
            select(-recent) %>%
            melt(id.vars = c("author", "n", "eps", "t"),
                 value.name = "post.p", variable.name = "prior.p")
      ggplot(user.summary2) + 
            geom_point(aes(t, eps, color=post.p), size=0.5, alpha=0.5) + 
            facet_wrap("prior.p") + 
            theme_bw() + 
            xlab("Average Days between Posts") +
            ylab("Days since Most Recent Post")
```

>>>>

Given that we cannot directly quantify the rate of suicide for online mental health boards, it is imperative that we develop a substitute to measure a similar construct. The construct that we propose is to estimate the total number of dropouts associated with suicidal ideation (SI).

@@

```{r, echo=FALSE, warning=FALSE}
### Load Data
      author.summary = 
            user.data %>% 
            group_by(author) %>%
            summarise(n = n()-1,
                      eps.bar = mean(time.last, na.rm=T),
                      t = as.numeric(october10 - max(date)),
                      si.author = si.author[1])
            filter(author.summary, !t < 150)
      n = author.summary$n
      eps = author.summary$eps.bar
      eps[is.na(eps)] = 0 
      t = author.summary$t
      N = nrow(author.summary)
      si = author.summary$si.author
### Simulate Mu given Data
      alpha = 1; beta = 1
      mu = replicate(n = 10000, rgamma(N, shape = alpha + n, rate = beta + n*eps))
### Now get overall credible interval for sum(Q)
      prior.p = 0.000001
      make.p = function(mu,p,t) p / (exp(-mu*t)*(1-p) + p)
      post.si = colSums(apply(mu[si,], 2, make.p, p=prior.p, t=t[si]))
      post.nosi = colSums(apply(mu[!si,], 2, make.p, p=prior.p, t=t[!si]))/sum(!si)*sum(si)
      post.excess = post.si - post.nosi
      hist(post.excess, main = "Posterior Distribution for\nExpected Reddit Drop-Outs per 100 SI-Positive Authors\n(Prior = 10e-4)",
           xlab="", ylab="")
      ci = quantile(post.excess, probs = c(0.025, 0.975))
```

@@

```{r, echo=FALSE, warning=FALSE}
### Calculate P(Q) from Mu and data
      prior.p = 10^-seq(0.5,15.5, by=0.5)
      post_p = sapply(prior.p, FUN = function(x){
            post.si = colSums(apply(mu[si,], 2, make.p, p=x, t=t[si]))
            post.nosi = colSums(apply(mu[!si,], 2, make.p, p=x, t=t[!si]))/sum(!si)*sum(si)
            post.excess = post.si - post.nosi
            return(quantile(post.excess, probs = c(0.025, 0.5, 0.975)))
      })
      colnames(post_p) = paste0("p10e-", seq(0.5,15.5, by=0.5))
      post_p = cbind(Percentile = rownames(post_p), as.data.frame(post_p))
      post_p = melt(post_p, id.vars = "Percentile", 
                    variable.name = "Prior P",
                    value.name = "Estimate")
      ggplot(post_p)

```
